Topic 21 Experiment and analysis

### 2018-05-11 Meetings/AnalysisMeetingMay2018/analysis_meeting2018_topic21.tex
Update for May meeting

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Topic 21 Experiment and analysis}
\date{17 May 2018}
\author[N.Vianello]{presented by N. Vianello on behalf of  MST1-Topic 21
  scientific team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \centering{
  Volker Naulin, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov,
Jernej Kovacic, Benoît Labit, Bruce Lipschultz, 
Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente, 
Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum, W. Vijvers}
j\end{frame}

@@

      % \includegraphics<7>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/ExampleShoulderAmplitude}
      % \includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsNe5IpConstantBt}
      % \includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsGreenwaldIpConstantBt}      
      % \includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantBt}

@@

        \item<6|only@6> We now consider the Target and upstream

@@

        \item<7|only@7> For both AUG and TCV flattening of normalized

@@

        % \item<7|only@7> Quantifying profile evolution using the
        %   \alert{shoulder amplitude metric} introduce by Wynn and
        %   Lipschultz for JET. \alert{Amplitude is the difference
        %     between normalized upstream density profiles}
        % \only<8-9>{\item Amplitude evolve faster in density at lower
        %   current in the far SOL \onslide<9>{\alert{but once evolution \textit{vs} greenwald
        %     fraction is considered the evolution is equivalent between
        %     different current}}}
        % \item<10|only@10> Amplitude evolution still reconciled in AUG if
        %   considered as a function of local evolution of $\Lambda_{div}$

>>>>

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{../biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Topic 21 Experiment and analysis}
\date{17 May 2018}
\author[N.Vianello]{presented by N. Vianello on behalf of  MST1-Topic 21
  scientific team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \centering{
  Volker Naulin, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov,
Jernej Kovacic, Benoît Labit, Bruce Lipschultz, 
Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente, 
Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum, W. Vijvers}
j\end{frame}

@@

      \includegraphics<8>[width=\textwidth]{../../Experiments/Comparison/pdfbox/ExampleShoulderAmplitude}
      \includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsNe5IpConstantBt}
      \includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsGreenwaldIpConstantBt}      
      \includegraphics<11>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantBt}

@@

        \item<only@6-7> We now consider the Target and upstream

@@

        \item<only@7> For both AUG and TCV flattening of normalized

@@

        \item<only@8> Quantifying profile evolution using the
          \alert{shoulder amplitude metric} introduce by Wynn and
          Lipschultz for JET \parencite{Wynn:2018gp}.
        \item<only@8>  \alert{Amplitude is the difference
            between normalized upstream density profiles}
        \item<only@8> Distinguishing behavior on the near and far SOL  
        \only<9-10>{\item Amplitude evolve faster in density at lower
          current in the far SOL \onslide<10>{\alert{but once evolution \textit{vs} greenwald
            fraction is considered the evolution is equivalent between
            different current.}
          \item \textcolor{ta3chameleon}{Still some inconsistency at lower
            current in agreement with different detachment evolution}}}
        \item<only@11> Amplitude evolution still reconciled in AUG if
          considered as a function of local evolution of $\Lambda_{div}$
